MultiDataImportPico

### 2023-12-07 Code/MultiDataImportPico.Rmd
Fixed file path in ProcessPico rmd
Removed redundant chunks. Added more annotations.

# Load Libraries and set Project Variables

```{r load libraries}
# libraries; Note check actual dependencies
library(tidyverse)
library(lubridate)
library(broom)
library(zoo)
library(data.table)
library(googledrive)
library(googlesheets4)
library(photobiologyWavebands)

@@

```{r set project variables}
#"..", takes up a level in the directory path
Project <- "PICO"
DataIn <- file.path("..", "Data", "RawData", "MultiCultiData.zip")
DataOut <- file.path("..","Data", "ImportedData", "MultiCultiData")

Skip <- 20

@@

# List previously imported MultiCulti files

```{r previously imported files}
list.files(path = DataOut, pattern = Project, full.names = TRUE)
```

# List MultiCulti files for Project that are saved in DataIn

```{r MultiCulti files}

@@

# Set Target File
```{r set TargetFile and read csv}

TargetFile <- "20221021_PICO_MCMIX006_RUN96.csv"

@@

## Create function using data.table::fread to skip the beginning comments and starts reading file after key word Skip

```{r fread_plus}
# fread_plus <- function(Flnm, Skip){data.table::fread(file = Flnm, skip = Skip) %>%
#     mutate(Filename = Flnm, CDateTime = ymd_hms(file.info(Flnm)$ctime))
# }
```

# Read in TargetFile

select(-c(V5)) only needed for some files.

```{r Read TargetFile}
# #abs-time is failing because it contains ',' in the variable values; file is actually a .tsv, not a .csv
# #abs-time not currently used?
# # TargetData <- fread_plus(Flnm = TargetFile, Skip = "key") %>%
# # select(-c(V5))
# 
# #run this if V5 is the 'value' column
# TargetData <- fread_plus(Flnm = TargetFile, Skip = "key")  %>%
#    select(-c(V5))
# TargetData <- fread_plus(Flnm = paste(DataIn, "20211223_PICO_MCMIX006_RUN42.csv", sep = ":"), Skip = "key")  %>%
#    select(-c(V5))
# # %>%
# #  select(-c(value)) %>%
# #   rename(value = V5)
# 
# 
# TargetData[1:10,]
# 
# #check whether all necessary values for 'key' are present; people forget to 'export all' values from PSI
# unique(TargetData$key)
```

@@

Run this chunk only for tubes with OD680 and/or OD720 < 0
This will keep record of tubes even if they did not grow or had negative growth. These tubes get filtered out later if you do not run this chunk
Remember to comment out after use 
```{r, Add dummy points if a tube has OD values less than zero}

@@

MAD is median absolute deviation Used median as opposed to mean to filter anomalous OD values due to affects of bubbling interference because determining outliers from the mean in a given window with many outliers were not detected since deviations from the mean were low. 
```{r filter bad OD and data points after experiment end time }

#moving average screen
MovAvgScreen <- 2 # 6
MovAvgWindow <- 2 # 20

@@

#rm(TargetDataMeta)
```
# check to confirm filter and ensure there are data points for all 8 tubes. If there is a missing tube, confirm that data was filtered out because OD680 and/or OD720 <0. If this is the case run the chunk "Add dummy points if a tube has OD values less than zero" above and rerun subsequent chunks.
```{r filterdataplot}

>>>>

# Load Libraries
```{r load libraries}
# libraries; Note check actual dependencies
library(tidyverse)
library(lubridate)
library(broom)
library(zoo)
library(data.table)
library(googledrive)
library(googlesheets4)
library(photobiologyWavebands)

@@

# Set Project Variables
```{r set project variables}
#"..", takes up a level in the directory path
Project <- "PICO"
DataIn <- file.path("..", "Data", "RawData", "MultiCultiData.zip")
DataOut <- file.path("..","Data", "ImportedData", "MultiCultiData")

# number of rows to skip upon read csv
Skip <- 20

@@

# List previously imported MultiCulti files
```{r previously imported files}
list.files(path = DataOut, pattern = Project, full.names = TRUE)
```

# List MultiCulti files for Project that are saved in DataIn
```{r MultiCulti files}

@@

# Set Target File and read in csv
```{r set TargetFile and read csv}

TargetFile <- "20211223_PICO_MCMIX006_RUN42.csv"

@@

@@

 Run this chunk only for tubes with OD680 and/or OD720 < 0 --> -->
This will keep record of tubes even if they did not grow or had negative growth. These tubes get filtered out later if you do not run this chunk.
Remember to comment out after use.
```{r, Add positive OD dummy points}

@@

MAD is median absolute deviation. Used median as opposed to mean to filter anomalous OD values due to affects of bubbling interference because determining outliers from the mean in a given window with many outliers were not detected since deviations from the mean were low. 
```{r filter bad OD and data points after experiment end time }

#moving average screen
MovAvgScreen <- 6 # 6
MovAvgWindow <- 20 # 20

@@

#rm(TargetDataMeta)
```

# check to confirm filter and ensure there are data points for all 8 tubes. If there is a missing tube, confirm that data was filtered out because OD680 and/or OD720 <0. If this is the case run the chunk "Add positive OD dummy points" above and rerun subsequent chunks.
```{r filterdataplot}
